Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

This is equivalent to using TD
to solve the modified Bellman equation with
rewards $r(s,a)-b-\alpha \E_{\rho^\pi}V$. Thus we are trying to solve
$r(s,a)-b-\alpha \E_{\rho^\pi}V+\gamma PV-V=0$, and the only fixed point
of this gradient step is
\begin{equation}
V(s)=V^{\pi_A}(s)-\frac{b+\E_{\rho^\pi} V^{\pi_A}}{1+\alpha-\gamma}
\end{equation}
% which looks different from the solution
% \begin{equation}
% V(s)=V^{\pi_A}(s)-\frac{b}{1-\gamma}
% \end{equation}
% considered above.
Meanwhile, $b$ is trained to minimize $\E_{s\sim \rho^\pi}
(r(s,a^\ast)-b+\gamma \E_{s'|s,a^\ast}V(s')-V(s))^2$ whose unique
solution given $V$ is TODO WRONG I THINK WE HAVE A DOUBLE SAMPLING
PROBLEM FOR $b$!!!
\begin{equation}
b=\E_{s\sim \rho^\pi}(r(s,a^\ast)+\gamma \E_{s'|s,a^\ast}V(s')-V(s))
\end{equation}
and substituting the fixed point
$V(s)=V^{\pi_A}(s)-\frac{b+\E V^{\pi_A}}{1-\gamma+\alpha}$ we find
\begin{equation}
b=-(\gamma-1) \frac{b+\E V^{\pi_A}}{1-\gamma+\alpha}
\end{equation}
which yields
\begin{equation}
b=\frac{1-\gamma}{\alpha} \E V^{\pi_A}
\end{equation}
contrary to $b=(1-\gamma)\E V^{\pi_A}$ we had before. 
This translates back to
\begin{equation}
V(s)=V^{\pi_A}(s)-\frac{b+\E_{\rho^\pi} V^{\pi_A}}{1+\alpha-\gamma}
=V^{\pi_A}(s)-\frac1\alpha \E_{\rho^\pi} V^{\pi_A}
\end{equation}
with this value of $b$.

@@

Meanwhile, $b$ is trained to minimize $\E_\rho (\E)$

>>>>

This is equivalent to using TD
to solve the modified Bellman equation with
rewards $r(s,a)-b-\alpha \E_{\rho^\pi}V$. Thus we are trying to solve
$r(s,a)-b-\alpha \E_{\rho^\pi}V+\gamma PV-V=0$, and the only fixed point
of this gradient step is
\begin{equation}
V(s)=V^{\pi_A}(s)-\frac{b+\E_{\rho^\pi} V^{\pi_A}}{1+\alpha-\gamma}
\end{equation}
% which looks different from the solution
% \begin{equation}
% V(s)=V^{\pi_A}(s)-\frac{b}{1-\gamma}
% \end{equation}
% considered above.
Meanwhile, $b$ is trained to minimize $\E_{s\sim
\rho^\pi}\E_{s'|s,a^\ast}
(r(s,a^\ast)-b+\gamma V(s')-V(s))^2$ whose unique
solution given $V$ is 
\begin{equation}
b=\E_{s\sim \rho^\pi}(r(s,a^\ast)+\gamma \E_{s'|s,a^\ast}V(s')-V(s))
\end{equation}
and substituting the fixed point
$V(s)=V^{\pi_A}(s)-\frac{b+\E V^{\pi_A}}{1-\gamma+\alpha}$ we find
\begin{equation}
b=-(\gamma-1) \frac{b+\E V^{\pi_A}}{1-\gamma+\alpha}
\end{equation}
which yields
\begin{equation}
b=\frac{1-\gamma}{\alpha} \E V^{\pi_A}
\end{equation}
contrary to $b=(1-\gamma)\E V^{\pi_A}$ we had before. 
This translates back to
\begin{equation}
V(s)=V^{\pi_A}(s)-\frac{b+\E_{\rho^\pi} V^{\pi_A}}{1+\alpha-\gamma}
=V^{\pi_A}(s)-\frac1\alpha \E_{\rho^\pi} V^{\pi_A}
\end{equation}
with this value of $b$.

@@

Meanwhile, $b$ is trained to minimize $\E_s\E_{s'|s,a}\E_{\tilde s} (r-b+\gamma
V(s')-V(s)+(1-\gamma)V(\tilde s))^2$ whose unique solution is
\begin{equation}
b=\E_s\E_{s'|s,a}\E_{\tilde s}(r+\gamma
V(s')-V(s)+(1-\gamma)V(\tilde s))
\end{equation}
Substituting the equilibrium value for $V$, $V=V^\pi+c$ yields
\begin{equation}
b=(1-\gamma)\E_{\tilde s} V^\pi(\tilde s)=(1-\gamma)\E_\rho V^\pi
\end{equation}
whatever $c$ is. Thus, for this optimal value of $b$, we have
\begin{equation}
V(s)=V^\pi(s)-\E_\rho V^\pi
\end{equation}
